Towards planning of infantile cardiac surgery based on simulation

### 2012-02-29 Doc/Miccai/shell-model.tex
missing commit of changed done yesterday
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@350 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

The bending property of the shell allows us to use smaller number of
elements for the simulation and use high polygonal model only for
visualisation. The convergence of the model is a key factor here. In our
experiments we were able to use only as few as eight nodes around the
circumference of a tubular model while still maintaining realistic
behaviour. Figure \ref{fig-convergence} shows the results for different
number of nodes along the circumference.

>>>>

The convergence of the model is a key factor here. In our
experiments we were able to use only as few as eight nodes around the
circumference of a tubular model while still maintaining realistic
behaviour. Figure \ref{fig-convergence} shows the results for different
number of nodes along the circumference.
As the model well-converges with relatively coarse meshes, we use 
a quite small number of elements for the simulation and use high polygonal model only for
visualisation.
